Training a Gaming Agent on Brainwaves

### 2020-09-27 review2/response.letter.tex

\section*{\fbox{Reviewer \#1 Transcript:}}

Comments to the Author
The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

Training a Gaming Agent on Brainwaves
The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
Page 1
The abstract still reads like an introduction until the last sentence.
I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”

\subsection*{\ovalbox{AE General Comments}}
AE's Comments to Author:

@@

Comments to the Author
The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

Training a Gaming Agent on Brainwaves
The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
Page 1
The abstract still reads like an introduction until the last sentence.  I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Expand the results of the paper as this is the contribution.
“Results show that there is an  \underline{effective} transfer of information and that the agent learns \underline{successfully} to solve the game efficiently.
Both the underlined terms need to cite evidence from the paper.

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 40 “This information is used to make a gaming agent $<$that$>$ improves ....”

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 11 col 2 “how biological agents learn from its $<$their$>$ environment by exploring it and getting feedback rewards, either negative or positive.”

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 17 col2 "\sout{Nonneglected} is the influence of DeepBrain’s AlphaGo project,” // Re-word

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, \sout{which} who is observing the robot, $<$to$>$ solve a task.”

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 58 Put in a reference number from ethics committee from which approval was sough (e.g. University committee)

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Page 2
Line 56 “Data \sout{is} $<$are$>$ handled and processed with the OpenVibe Designer,” // datum-data

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 37 col 2 “This dataset has been published on the IEEE DataPort initiative [15].” // I would move this to the end of next paragraph (or possibly end of paper)

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Page 4
Lin 24 This allows \sout{to learn} the Q-Table $<$to learn$>$ based on the subject’s feedback from the movements the agent
took, which are chosen pseudo-randomly, while executing the brainwave session.

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 50 “The best overall performance is obtained using Logistic Regression.” // also need to discuss the significance of the overall levels of accuracy in Discussion. Is a best performance of 0.672 useful/acceptable? How does it compare to other researchers (if a comparison is possible).

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 42 col 2 “These results are also consistent with their classification ROC curves, shown \sout{on} $<$in$>$ Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one. This would provide the basis for comparison.

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Page 5
Figure 5 “Y axis shows the averaged number of steps, while x axis show the number of
experiences used to cumulative train the Q-Table.”
// Why does Fig5 E only have 2 sets of data? Some discussion of the (smaller) change from 1 – 2 would be appropriate (e.g. I Discussion)
Line 51 “No\sout{t} performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.” // useless is not a good choice of wording –provides no value

@@

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Line 20 col 2 Despite that, the rewards generated from different subjects can be used to train the same Q- Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
//These are key findings, worth more discussion/interpretation and inclusion in abstract.

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

\subsection*{\ovalbox{Reviewer 2 General Comments}}

The authors have satisfactorily addressed my concerns. I have a minor comment regarding Figure 3. It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant. Please clarify. I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.

### 2020-10-11 review2/response.letter.tex

Comments to the Author
The authors have satisfactorily addressed my concerns. I have a minor comment regarding Figure 3. It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant. Please clarify. I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.

\subsection*{\ovalbox{AE General Comments}}
AE's Comments to Author:

Associate Editor
Comments to the Author:
The paper is improved but would benefit from a further update to
- improve abstract

\begin{quotation}
{\color{blue}
Rewrote the abstract talking in further detail obtained results.
}
\end{quotation}

@@

Training a Gaming Agent on Brainwaves
The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
Page 1
The abstract still reads like an introduction until the last sentence.  I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”

\begin{quotation}
{\color{blue}
Rewrote the abstract talking in further detail obtained results.
}
\end{quotation}

Expand the results of the paper as this is the contribution.
“Results show that there is an  \underline{effective} transfer of information and that the agent learns \underline{successfully} to solve the game efficiently.
Both the underlined terms need to cite evidence from the paper.

\begin{quotation}
{\color{blue}
This was solved in a previous version.
}
\end{quotation}

@@

Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, \sout{which} who is observing the robot, $<$to$>$ solve a task.”

\begin{quotation}
{\color{blue}
Fixed issue.
}
\end{quotation}

Line 58 Put in a reference number from ethics committee from which approval was sough (e.g. University committee)

\begin{quotation}
{\color{blue}
TODO: No entiendo esto bien a que se refiere
}
\end{quotation}

@@

Page 2
Line 56 “Data \sout{is} $<$are$>$ handled and processed with the OpenVibe Designer,” // datum-data

\begin{quotation}
{\color{blue}
Fixed issue for all appeareances of "data is".
}
\end{quotation}

@@

Line 37 col 2 “This dataset has been published on the IEEE DataPort initiative [15].” // I would move this to the end of next paragraph (or possibly end of paper)

\begin{quotation}
{\color{blue}
Added information in the form of a footnote.
}
\end{quotation}

@@

Page 4
Lin 24 This allows \sout{to learn} the Q-Table $<$to learn$>$ based on the subject’s feedback from the movements the agent
took, which are chosen pseudo-randomly, while executing the brainwave session.

\begin{quotation}
{\color{blue}
Fixed issue.
}
\end{quotation}

Line 50 “The best overall performance is obtained using Logistic Regression.” // also need to discuss the significance of the overall levels of accuracy in Discussion. Is a best performance of 0.672 useful/acceptable? How does it compare to other researchers (if a comparison is possible).

\begin{quotation}
{\color{blue}
AC'a hablar que es aceptable porqeu alcanza para aprender el optimal policy. Buscar una comparaci'on?
}
\end{quotation}

@@

Line 42 col 2 “These results are also consistent with their classification ROC curves, shown \sout{on} $<$in$>$ Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one. This would provide the basis for comparison.

\begin{quotation}
{\color{blue}
TODO: Arregle error gramatical pero no agregu'e la ROC mala.
}
\end{quotation}

@@

This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning. The collected data show that ErrP signals can in fact be classified and used to train an agent effectively. // Can you link these findings to confirm/challenge other recent research in Err potentials

\begin{quotation}
{\color{blue}
fdsjlfjldksj
}
\end{quotation}

Page 6
Fig 8 – why use data from subject 6 (a non-learner)?

\begin{quotation}
{\color{blue}
Subject 5 and 6 aren't used to train the algorithm in this instance. Added this information in the figure caption.
}
\end{quotation}

### 2020-10-11 ErrP.tex
Add grammatical fixes to paper and included an improved version of the abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error. We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent playing randomly a game. The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance. Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

@@

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person that is observing a robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}. Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{Images/complete_flow.png}
    \caption{Overview of the experimental procedure. Brainwaves are obtained by the OpenVibe Acquisition Server.  The Game Manager is responsible for generating the game screen, the game mechanics, and the game movements performed by the gaming agent.  It is also connected to the Acquisition Server to send stimulus information.  The captured information is stored by the OpenVibe Designer.  Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.  This information is used by a Reinforcement Learning algorithm to learn iteratively a Q-Table to improve the performance of the agent that plays the game.}
    \label{diag:complete_flow}
\end{figure*}

@@

Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$~Hz. A $50$~Hz notch filter is applied to filter out power line noise. An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied. Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel to record the stimulus, which corresponds to a game movement performed by the agent.  After everything is connected, the subject is seated in a comfortable chair in front of a computer screen. The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.  This dataset has been published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.

The Acquisition Server receives and synchronizes the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application. When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server. A brainwave session consists of several matches, each one being a gameplay.  In the end, the sequence of game movements and the signal data generated for each match are saved for offline processing.

@@

%The first step in order to be able to find ErrP signals is to choose the most efficient algorithm, and the proper calibration. In order to do this different parameters are tested for a set of algorithms and for each individual subject. Initially a sub-selection of experiments is used to define a subset of parameters to test with, and then all the data is tested with this subset of parameters.

@@

After the raw data is loaded and tagged, epochs are extracted. Epochs consist of all the sample points that take place during the 2 seconds from the start of the event, 2 seconds corresponding to the time it takes for each action to take place, resulting in 500 samples per channel, as the sampling frequency is 250 Hz. Thus, each epoch is composed of a matrix $500$ x $8$ channels.

@@

In this way, the raw data of a brainwave session is processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e. if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit). The ErrP is expected to be found in hits. To get the data ready for classification, the stimulus channel is removed to classify the signals using only the EEG data. Each epoch is regularized using a MinMaxScaler, i.e. subtracting the minimum value in the epoch and dividing by the signal peak-to-peak amplitude~\cite{Zhou2019}.  The eight channels are concatenated using the MNE Vectorizer function, which transforms the data matrix into a single array sample. Lastly, this data is used by the classification module as information to train and test a classifier. Five different classification algorithms are used:  Logistic Regression, Multilayer Perceptron with a hidden layer of 100 neurons (i.e. default values for the Scikit-Learn MLPClassifier), Random Forest, KNeighbours with k=3 and finally a linear kernel Support Vector Classifier (i.e. SVM)~\cite{Lotte2018}.

@@

In the case for OHC 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively. Figures \ref{fig:avg_steps} for OHC 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.  These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.  Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.  This variation in performance for different OHCs has been studied extensively in BCI~\cite{Chavarriaga2014}.  Besides low data samples, there are other reasons affecting the classification accuracy:  cognitive reasons (i.e. the OHC not paying extensively attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs. X axis show the progressive number of gaming agent training matches used to train the Q-Table.}
\label{fig:avg_steps_all}
\end{figure}

@@

%Brainwave sessions have a low amount of matches in order to reduce fatigue from OHCs. However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier. Matches from OHCs with the largest amounts of data have the best classification scores and produced more accurate rewards. This can also be achieved designing a bigger game system that generates more samples with every session.  While classifying, the better performing classifier is Logistic Regression.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
%objective
Error-related potential (ErrP) are a particular type of ERP elicited by a person attending a recognizable error. The purpose of this study is to determine if these signals can be used to train a Reinforcement Learning (RL) algorithm to learn an optimal policy. A game scenario is used to trigger the feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic (OHC) that observes an agent playing a game. ErrP signals are captured using a Brain-Computer Interface (BCI) system.
%method
The experimental process consists of an individual observing a simple game scenario while their brain signals are captured. The game consists of a grid, where the object has to reach a desired target in the fewest amount of steps. Initially the object moves randomly within the grid,
and a RL algorithm is trained for it to learn the optimal policy, in order to know how to reach the target in the least amount of steps.
%Results
% Expand the results of the paper as this is the contribution. “Results show that there is an effective transfer of information and that the agent learns successfully to solve the game eﬀiciently. Both the underlined terms need to cite evidence from the paper.
% The rewards generated from different subjects can be used to train the same Q- Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time. //These are key findings, worth more discussion/interpretation and inclusion in abstract.
Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently. Initially when the game is simulated with random movements it takes the agent an average of 97 steps to reach the objective, whereas when the trained Q-Table is used to reach the objective, the agent can reach the goal in the optimal number of steps, which is 8 steps. The algorithm can be trained with information from different OHCs, since the resulting dataset is composed of rewards for each corresponding step, independent of who they were generated from. This shows that the error classification accuracy (approximately 0.67) is good enough for the algorithm to learn. The reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect the accuracy, they only make the learning process slower.
%conclusions
This study shows that: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.

% In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error. We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent playing randomly a game. The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance. Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

@@

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution. The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.  Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}. Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.  Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{Images/complete_flow.png}
    \caption{Overview of the experimental procedure. Brainwaves are obtained by the OpenVibe Acquisition Server.  The Game Manager is responsible for generating the game screen, the game mechanics, and the game movements performed by the gaming agent.  It is also connected to the Acquisition Server to send stimulus information.  The captured information is stored by the OpenVibe Designer.  Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.  This information is used by a Reinforcement Learning algorithm that iteratively trains a Q-Table in order to improve the performance of the agent that plays the game.}
    \label{diag:complete_flow}
\end{figure*}

@@

Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$~Hz. A $50$~Hz notch filter is applied to filter out power line noise. An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied. Data are handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel to record the stimulus, which corresponds to a game movement performed by the agent.  After everything is connected, the subject is seated in a comfortable chair in front of a computer screen. The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.

The Acquisition Server receives and synchronizes the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application. When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server. A brainwave session consists of several matches, each one being a gameplay.  In the end, the sequence of game movements and the signal data generated for each match are saved for offline processing \footnote{The brainwave dataset has been published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.}.

@@

%The first step in order to be able to find ErrP signals is to choose the most efficient algorithm, and the proper calibration. In order to do this different parameters are tested for a set of algorithms and for each individual subject. Initially a sub-selection of experiments is used to define a subset of parameters to test with, and then all the data are tested with this subset of parameters.

@@

After the raw data are loaded and tagged, epochs are extracted. Epochs consist of all the sample points that take place during the 2 seconds from the start of the event, 2 seconds corresponding to the time it takes for each action to take place, resulting in 500 samples per channel, as the sampling frequency is 250 Hz. Thus, each epoch is composed of a matrix $500$ x $8$ channels.

@@

In this way, the raw data of a brainwave session is processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e. if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit). The ErrP is expected to be found in hits. To get the data ready for classification, the stimulus channel is removed to classify the signals using only the EEG data. Each epoch is regularized using a MinMaxScaler, i.e. subtracting the minimum value in the epoch and dividing by the signal peak-to-peak amplitude~\cite{Zhou2019}.  The eight channels are concatenated using the MNE Vectorizer function, which transforms the data matrix into a single array sample. Lastly, this data are used by the classification module as information to train and test a classifier. Five different classification algorithms are used:  Logistic Regression, Multilayer Perceptron with a hidden layer of 100 neurons (i.e. default values for the Scikit-Learn MLPClassifier), Random Forest, KNeighbours with k=3 and finally a linear kernel Support Vector Classifier (i.e. SVM)~\cite{Lotte2018}.

@@

In the case for OHC 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively. Figures \ref{fig:avg_steps} for OHC 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.  These results are also consistent with their classification ROC curves, shown in Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.  Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.  This variation in performance for different OHCs has been studied extensively in BCI~\cite{Chavarriaga2014}.  Besides low data samples, there are other reasons affecting the classification accuracy:  cognitive reasons (i.e. the OHC not paying extensively attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs. X axis show the progressive number of gaming agent training matches used to train the Q-Table. These matches correspond to all subjects, excluding subjects 5 and 6 which individually show no significant learning progress.}
\label{fig:avg_steps_all}
\end{figure}

@@

%Brainwave sessions have a low amount of matches in order to reduce fatigue from OHCs. However data suggests that longer sessions are required in order to reach better classification scores, since more data are available in order to train the classifier. Matches from OHCs with the largest amounts of data have the best classification scores and produced more accurate rewards. This can also be achieved designing a bigger game system that generates more samples with every session.  While classifying, the better performing classifier is Logistic Regression.
